\bf A Hierarchical Model for Heterogenous Reliability Field Data

### 2018-05-14 paper/m-lb-m-technometrics.tex
Complete edits based on May 13 meeting, and add drive brand names to Supplemental Material

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption, url}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

\section{Introduction}
\subsection{Motivation}
Consumers have an interest in accurate assessment of product reliability. Toward this end, there usually is a need for models that can accommodate common failure patterns and methods which can make the most of available data and properly account for uncertainty. Doing these things well enables good decision-making in matters related to product life, including purchase decisions and contingency planning.
%While computationally convenient, simple lifetime models can fail at each of these.

@@

\begin{figure}[H]
  %\includegraphics[width=.9\textwidth]{data-sum.pdf}
  \includegraphics[width=.9\textwidth]{dm-summ-scatter.pdf}
  \caption{Scatterplot of total observed running time (hundred thousands of hours) versus total number of observed failures.  Each number labels a unique drive-model, numbered between 1 and 44.   Axes are on the log scale.}
  \label{drive-scatter}
\end{figure}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=.6\textwidth]{km14-prob}
  \caption{K-M estimate for Drive-model 14.  Uncertainty band correspond to pointwise standard errors (using Greenwood's formula.)}
  \label{fig1}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrr}
  \hline
 & Lower & Estimate & Upper \\ 
  \hline
$\pi$ & 0.033 & 0.054 & 0.099 \\ 
 $\beta_1 = 1/\sigma_1 $ & 0.47 & 1.13 & 1.72 \\ 
  $\beta_2 = 1/\sigma_2$ & 4.47 & 4.70 & 4.95 \\ 
  $t_{0.5,1}$ & $1.03$  & $2.28$ & $3.99$\\ 
  $t_{0.2,2}$ & $18.0$ & $18.2$ & $18.6$ \\ 
   \hline
\end{tabular}
\caption{Posterior 95\% Credible Intervals for the 5 GLFP parameters for Drive-model 14.  The quantiles are in thousands of hours.}
\label{table:1}
\end{table}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=.8\textwidth]{km14-prob-plus}
  \caption{The estimated GLFP model for Drive-model 14 plotted on Weibull paper.  The dashed line corresponds to the median of the posterior draws; pointwise 90\% credible bounds are indicated by the smooth region.  The solid line is an adjusted K-M estimate with pointwise 90\% credible bounds in blue.}
  \label{ex1-overlay}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{heterogeneity-compare}
\caption{Left: Adjusted K-M estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median cdf estimates for Models 1-4, ordered left to right, top to bottom.}
\label{fig:fig2}
\end{figure}

@@

\begin{figure}[H]
{\centering
\includegraphics[width=\textwidth]{single-drive-4-Models-ex-v2}}
\caption{Posterior median of the proportion failing as a function of time under Models 1-4 for sample of drive-models, with axes scales as for Weibull probability plotting.  The solid step function is the adjusted K-M estimate.}
\label{fig:mod_comp_leg}
\end{figure}

@@

\begin{figure}
\begin{table}[H]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & $\widehat{\text{elpd}}$ \ & Difference in $\widehat{\text{elpd}}$ \ & SE of the Difference & Effective No. Parameters\\ 
  \hline
Model 4 & -13309.5 & 40.7 & 11.3 & 92.5 \\ 
Model 3 & -13350.2 & 458.8 & 31.0 & 68.8 \\ 
Model 2 & -13809.0 & 3674.6 & 96.2 & 49.6 \\ 
Model 1 & -17483.6 &  &  & 4.3 \\
   \hline
\end{tabular}
\caption{Expected log pointwise predictive density (elpd) and related statistics for each model.}
\label{table:2}
\end{table}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{ppcheck-sample}
\caption{Adjusted K-M estimates of the proportion failing for a representative subset of drive-models. Both the original data (\textbf{bold} line) and 19 ``replicated" data sets from the posterior predictive distribution (\textit{dashed} lines) are shown.}
\label{fig:post-pred-KM}
\end{figure}

@@

\begin{figure}[H]
\centering
   \begin{subfigure}[b]{0.80\textwidth}
   \includegraphics[width=1\linewidth]{b10new.pdf}
   \caption{Point estimate and 50\% CI for $t_{0.10}$}
   \label{fig:Ng1} 
\end{subfigure}

\begin{subfigure}[b]{0.80\textwidth}
   \includegraphics[width=1\linewidth]{pinew.pdf}
   \caption{Point estimate and 50\% CI for $\pi$}
   \label{fig:Ng2}
\end{subfigure}

\caption{(a) 50\% CI (in years) for $t_{0.10}$ (b) 50\% CI for $\pi$ plotted on the logit scale.  Both plots are sorted based on the median value of the marginal posterior distribution of $t_{0.10}$.}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{dm-eval}
  \caption{Left: 90\% CI of the posterior predictive distributions for $e^{-0.4 t_{g,new}}$ the depreciated value at failure (VAF) for a new unit for each Drive-model.
  Right: A comparison (90\% CI) of the predictive distribution of TTF in hundreds of thousands of hours (top) and VAF (bottom) based on 40\% depreciation for the best 11 drive-models, shows that rankings produced by the two measures are not equivalent.}
  \label{fig5}
\end{figure}

@@

The mean time-to-failure (MTTF) for drive-model $d$ can be estimated by
$$\frac{1}{S} \sum_{s=1}^{S} t_{g,new}^{(s)}.$$

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{accuracy_compare}
  \caption{Posterior distributions of 0.1 quantiles for a representative subset of drive-models where separate fitting of the GLFP model was successful (unimodal posteriors and passing MCMC convergence diagnostics.) $r$ indicates the number of observed failures. Separate fits use the same priors as Model 4, but have greater uncertainty because there is no borrowing of information across drive-models.}

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption, url, makecell}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

\section{Introduction}
\subsection{Motivation}
Consumers have an interest in accurate assessment of product reliability. Toward this end, there usually is a need for models that can accommodate common failure patterns and methods which can make the most of available data and properly account for uncertainty. Doing these things well enables good decision-making in matters related to product life, including purchase decisions and contingency planning.

@@

\begin{figure}[H]
  %\includegraphics[width=.9\textwidth]{data-sum.pdf}
  \includegraphics[width=.9\textwidth]{dm-summ-scatter.pdf}
  \caption{\footnotesize Scatterplot of total observed running time (hundred thousands of hours) versus total number of observed failures.  Each number labels a unique drive-model, numbered between 1 and 44.   Axes are on the log scale.}
  \label{drive-scatter}
\end{figure}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=.6\textwidth]{km14-prob}
  \caption{\footnotesize K-M estimate for Drive-model 14.  Uncertainty band correspond to pointwise standard errors (using Greenwood's formula.)}
  \label{fig1}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrr}
  \hline
 & Lower & Estimate & Upper \\ 
  \hline
$\pi$ & 0.033 & 0.054 & 0.099 \\ 
 $\beta_1 = 1/\sigma_1 $ & 0.47 & 1.13 & 1.72 \\ 
  $\beta_2 = 1/\sigma_2$ & 4.47 & 4.70 & 4.95 \\ 
  $t_{0.5,1}$ & $1.03$  & $2.28$ & $3.99$\\ 
  $t_{0.2,2}$ & $18.0$ & $18.2$ & $18.6$ \\ 
   \hline
\end{tabular}
\caption{\footnotesize Posterior 95\% Credible Intervals for the 5 GLFP parameters for Drive-model 14.  The quantiles are in thousands of hours.}
\label{table:1}
\end{table}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=.8\textwidth]{km14-prob-plus}
  \caption{\footnotesize The estimated GLFP model for Drive-model 14 plotted on Weibull paper.  The dashed line corresponds to the median of the posterior draws; pointwise 90\% credible bounds are indicated by the smooth region.  The solid line is an adjusted K-M estimate with pointwise 90\% credible bounds in blue.}
  \label{ex1-overlay}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{heterogeneity-compare}
\caption{\footnotesize Left: Adjusted K-M estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median cdf estimates for Models 1-4, ordered left to right, top to bottom.}
\label{fig:fig2}
\end{figure}

@@

\begin{figure}[H]
{\centering
\includegraphics[width=\textwidth]{single-drive-4-Models-ex-v2}}
\caption{\footnotesize Posterior median of the proportion failing as a function of time under Models 1-4 for sample of drive-models, with axes scales as for Weibull probability plotting.  The solid step function is the adjusted K-M estimate.}
\label{fig:mod_comp_leg}
\end{figure}

@@

\begin{figure}
\begin{table}[H]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & $\widehat{\text{elpd}}$ \ & \thead{Estimated Difference \\ in $\widehat{\text{elpd}}$} \ & \thead{Standard Error of \\ the Difference} & \thead{Effective Number of \\ Parameters}\\ 
  \hline
Model 4 & -13309.5 & 40.7 & 11.3 & 92.5 \\ 
Model 3 & -13350.2 & 458.8 & 31.0 & 68.8 \\ 
Model 2 & -13809.0 & 3674.6 & 96.2 & 49.6 \\ 
Model 1 & -17483.6 &  &  & 4.3 \\
   \hline
\end{tabular}
\caption{\footnotesize Expected log pointwise predictive density (elpd) and related statistics for each model.}
\label{table:2}
\end{table}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{ppcheck-sample}
\caption{\footnotesize Adjusted K-M estimates of the proportion failing for a representative subset of drive-models. Both the original data (\textbf{bold} line) and 19 ``replicated" data sets from the posterior predictive distribution (\textit{dashed} lines) are shown.}
\label{fig:post-pred-KM}
\end{figure}

@@

\begin{figure}[H]
\centering
   \begin{subfigure}[b]{0.80\textwidth}
   \includegraphics[width=1\linewidth]{b10new.pdf}
   \caption{\footnotesize Point estimate and 50\% CI for $t_{0.10}$}
   \label{fig:Ng1} 
\end{subfigure}

\begin{subfigure}[b]{0.80\textwidth}
   \includegraphics[width=1\linewidth]{pinew.pdf}
   \caption{\footnotesize Point estimate and 50\% CI for $\pi$}
   \label{fig:Ng2}
\end{subfigure}

\caption{\footnotesize (a) 50\% CI (in years) for $t_{0.10}$ (b) 50\% CI for $\pi$ plotted on the logit scale.  Both plots are sorted based on the median value of the marginal posterior distribution of $t_{0.10}$.}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{dm-eval}
  \caption{\footnotesize Left: 90\% CI of the posterior predictive distributions for $e^{-0.4 t_{g,new}}$ the depreciated value at failure (VAF) for a new unit for each Drive-model.
  Right: A comparison (90\% CI) of the predictive distribution of TTF in hundreds of thousands of hours (top) and VAF (bottom) based on 40\% depreciation for the best 11 drive-models, shows that rankings produced by the two measures are not equivalent.}
  \label{fig5}
\end{figure}

@@

The mean time-to-failure (MTTF) for drive-model $d$ can be estimated by
$$\frac{1}{S} \sum_{s=1}^{S} t_{g,new}^{(s)}.$$
where $t_{g,new}^{(s)}$ is a draw from the posterior predictive distribution for drive-model $g$.

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{accuracy_compare}
  \caption{\footnotesize Posterior distributions of 0.1 quantiles for a representative subset of drive-models where separate fitting of the GLFP model was successful (unimodal posteriors and passing MCMC convergence diagnostics.) $r$ indicates the number of observed failures. Separate fits use the same priors as Model 4, but have greater uncertainty because there is no borrowing of information across drive-models.}

### 2018-05-14 paper/supplement.tex
Complete edits based on May 13 meeting, and add drive brand names to Supplemental Material

>>>>

\section{Drive Model Brands}
Below are the brand names (provided by Backblaze) corresponding to
the model numbers used in the analysis.
\begin{table}[H]
\centering
\begin{tabular}{lr}
  \hline
Brand Name & Model ID \\ 
  \hline
HGST HDS5C4040ALE630 &   1 \\ 
  HGST HMS5C4040ALE640 &   2 \\ 
  HGST HMS5C4040BLE640 &   3 \\ 
  Hitachi HDS5C3030ALA630 &   4 \\ 
  Hitachi HDS5C4040ALE630 &   5 \\ 
  Hitachi HDS722020ALA330 &   6 \\ 
  Hitachi HDS723020BLA642 &   7 \\ 
  Hitachi HDS723030ALA640 &   8 \\ 
  ST1500DL003 &   9 \\ 
  ST2000DL001 &  10 \\ 
  ST2000DL003 &  11 \\ 
  ST250LM004 HN &  12 \\ 
  ST250LT007 &  13 \\ 
  ST3000DM001 &  14 \\ 
  ST31500341AS &  15 \\ 
  ST31500541AS &  16 \\ 
  ST3160316AS &  17 \\ 
  ST3160318AS &  18 \\ 
  ST32000542AS &  19 \\ 
  ST320005XXXX &  20 \\ 
  ST320LT007 &  21 \\ 
  ST33000651AS &  22 \\ 
  ST4000DM000 &  23 \\ 
  ST4000DX000 &  24 \\ 
  ST500LM012 HN &  25 \\ 
  ST6000DX000 &  26 \\ 
  ST9250315AS &  27 \\ 
  TOSHIBA DT01ACA300 &  28 \\ 
  TOSHIBA MD04ABA400V &  29 \\ 
  WDC WD10EACS &  30 \\ 
  WDC WD10EADS &  31 \\ 
  WDC WD10EADX &  32 \\ 
  WDC WD1600AAJB &  33 \\ 
  WDC WD1600AAJS &  34 \\ 
  WDC WD1600BPVT &  35 \\ 
  WDC WD20EFRX &  36 \\ 
  WDC WD30EFRX &  37 \\ 
  WDC WD30EZRX &  38 \\ 
  WDC WD3200BEKX &  39 \\ 
  WDC WD5000LPVX &  40 \\ 
  WDC WD60EFRX &  41 \\ 
  WDC WD800AAJB &  42 \\ 
  WDC WD800BB &  43 \\ 
  WDC WD800JB &  44 \\ 
   \hline
\end{tabular}
\end{table}
